### 2016-11-03 capability-machine.tex
Typos

\documentclass{article}
\usepackage[utf8]{inputenc}

@@

\newcommand{\forcenewline}{$\phantom{v}$\\}

@@

\caption{The permissions in this capability system}
\label{tab:permission-list}
\end{table}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (7) {$\rwlx$};
    \node[main node] (8) [below left of=7] {$\readwritel$};
    \node[main node] (1) [below right of=7] {$\rwx$};
    \node[main node] (2) [below right of=1] {$\exec$};
    \node[main node] (3) [below of=2] {$\entry$};
    \node[main node] (4) [below left of=1] {$\readwrite$};
    \node[main node] (5) [below of=4] {$\readonly$};
    \node[main node] (6) [below right of=5] {$\noperm$};

  \path[every node/.style={font=\sffamily\small}]
    (7) edge (8)
    (7) edge (1)
    (8) edge (4)
    (1) edge (2)
    (2) edge (3)
    (3) edge (6)
    (1) edge (4)
    (4) edge (5)
    (5) edge (6);
\end{tikzpicture}

@@

\section{Logical Relation'}
\subsection{Worlds}
Assume $\Worstr$ and $\Worwk$ are preordered \cofes{} and $\xi_{\var{wk}}$ and $\xi_{\var{str}}$ are isomorphisms such that
\begin{align*}
  \xi_{\var{wk}} :   \Worwk \cong \blater (\nats \finparfun (&\{\revoked\} \union \\
                                           & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \union \\
                                           & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{wk}}}) \\ \\
  \xi_{\var{str}} :   \Worstr \cong (\nats \finparfun \blater (&\{\revoked\} \union \\
                                           & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \union \\
                                           & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{str}}})
\end{align*}
We now define the regions to be
\begin{align*}
  \Regions = & \{\revoked\} \union \\
             & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \union \\
             & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments}))
\end{align*}
And the worlds are
\[
  \Worlds = \RegionNames \finparfun \Regions
\]
Where $\RegionNames = \nats$.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq \lambda \_ \ldotp(\temp,(\start,\addrend),=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; (\start,\addrend) \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,(\start,\addrend),=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
  \right\}
\end{align*}
\lau{In the above $H$ definitions, $\hat{W}$ is not a world, so there is a type problem that needs to be fixed. Maybe solve the recursive domain equations wrt the worlds instead.}

For convenience define
\begin{align*}
  \localReg & \defeq \dom(\erase{W}{\perm,\temp}) \\
  \globalReg & \defeq \dom(\erase{W}{\perm})
\end{align*}
$\localReg$ are the regions that local capabilities may govern. $\globalReg$ are the regions that global capabilities may govern. Now define the following function
\[
  \var{localityReg}(\gl) \defeq 
  \begin{cases}
    \localReg & \gl = \local \\
    \globalReg & \gl = \glob
  \end{cases}
\]

\begin{align*}
    & \writeCond{} : ((\Views \rightharpoonup \Regions) \times \Globals) \fun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats}  \\
    & \writeCond{}(\iota,\gl)(\start,\addrend,W) =  \\
    & \quad \begin{aligned}[t]
              \{ n \mid & \;\exists r \in \var{localityReg}(g) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nequal[n-1] \iota_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}

\begin{align*}
    & \readCond{}(\gl)(\start,\addrend,W) =  \\
    & \quad \begin{aligned}[t]
              \{ n \mid & \;\exists r \in \var{localityReg}(g) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsubeq[n-1] \iota^{\var{pwl}}_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}
\lau{I am in doubt whether it should be $\iota^{\var{pwl}}$ in the read condition.}

@@

\begin{align*}
  \stdkr : &  \Worlds \monwknefun \UPred{\Words} \\
  \stdkr \defeq & \lambda \stdvr \ldotp \lambda W \ldotp\{ \npair{c} \mid
                     \begin{aligned}[t]
                       & \npair{c} \in \stdvr(W) \land \\
                       &  \forall W' \futurewk W, n' < n\ldotp
                       \forall \heapSat[\hs]{n'}{W'} \ldotp \forall \reg, \npair[n']{\reg} \in \stdrr(\stdvr)(W') \ldotp \\
                       & \quad \npair[n']{(\reg\update{\pcreg}{\updatePcPerm{\var{c}}},\hs)} \in \observations(W') \}
                 \end{aligned}
\end{align*}

\begin{align*}
  \stder : & \Worlds \nefun \UPred{\Words} \\
  \stder \defeq & \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(\stdvr)(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(\stdvr)(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}

>>>>

\documentclass[a4paper]{article}
%\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc}

@@

\newcommand{\forcenewline}{$\phantom{v}$\\}
\newcommand{\judgment}[2]{\paragraph{#1}\hspace{\stretch{1}}\fbox{$#2$}}

@@

\caption{The permissions in this capability system}
\label{tab:permission-list}
\end{table}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (7) {$\rwlx$};
    \node[main node] (8) [below left of=7] {$\readwritel$};
    \node[main node] (1) [below right of=7] {$\rwx$};
    \node[main node] (2) [below right of=1] {$\exec$};
    \node[main node] (3) [below right of=2] {$\entry$};
    \node[main node] (4) [below left of=1] {$\readwrite$};
    \node[main node] (5) [below right of=4] {$\readonly$};
    \node[main node] (6) [below right of=5] {$\noperm$};

  \path[every node/.style={font=\sffamily\small}]
    (7) edge (8)
    (7) edge (1)
    (8) edge (4)
    (1) edge (2)
    (2) edge (3)
    (2) edge (5)
    (3) edge (6)
    (1) edge (4)
    (4) edge (5)
    (5) edge (6);
\end{tikzpicture}

@@

\section{Logical Relation'}
\subsection{Worlds}
Assume $\Worstr$ and $\Worwk$ are preordered \cofes{} and $\xi_{\var{wk}}$ and $\xi_{\var{str}}$ are isomorphisms such that
\begin{align*}
  \xi_{\var{wk}} :   \Worwk \cong \blater (\nats \finparfun (   & \{\revoked\} + \\
                                                                & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) + \\
                                                                & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{wk}}}) \\ \\
  \xi_{\var{str}} :   \Worstr \cong \blater (\nats \finparfun ( & \{\revoked\} + \\
                                                                & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) + \\
                                                                & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{str}}})
\end{align*}
We now define the regions to be
\begin{align*}
  \Regions = & \{\revoked\} \uplus \\
             & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \uplus \\
             & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments}))
\end{align*}
And the worlds are
\[
  \Worlds = \RegionNames \finparfun \Regions
\]
Where $\RegionNames = \nats$.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq \lambda \_ \ldotp(\temp,(\start,\addrend),=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; (\start,\addrend) \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,(\start,\addrend),=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; (\start,\addrend) \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
  \right\}
\end{align*}
\lau{In the above $H$ definitions, $\hat{W}$ is not a world, so there is a type problem that needs to be fixed. Maybe solve the recursive domain equations wrt the worlds instead.}

For convenience define
\begin{align*}
  \localReg(W) & \defeq \dom(\erase{W}{\perm,\temp}) \\
  \globalReg(W) & \defeq \dom(\erase{W}{\perm})
\end{align*}
$\localReg$ are the regions that local capabilities may govern - that is permanent and global regions. $\globalReg$ are the regions that global capabilities may govern - that is permanent regions. Now define the following function
\[
  \var{localityReg}(\gl,W) \defeq 
  \begin{cases}
    \localReg(W) & \text{if } \gl = \local \\
    \globalReg(W) & \text{if } \gl = \glob
  \end{cases}
\]

\begin{align*}
    & \writeCond{} : ((\Views \rightharpoonup \Regions) \times \Globals) \fun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats}  \\
    & \writeCond{}(\iota,\gl)(\start,\addrend,W) =  \\
    & \quad \begin{aligned}[t]
              \{ n \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nequal[n-1] \iota_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}

\begin{align*}
    & \readCond{}(\gl)(\start,\addrend,W) =  \\
    & \quad \begin{aligned}[t]
              \{ n \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsubeq[n-1] \iota^{\var{pwl}}_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}
\lau{I am in doubt whether it should be $\iota^{\var{pwl}}$ in the read condition.}

@@

\begin{align*}
  \stdkr : &  \Worlds \monwknefun \UPred{\Words} \\
  \stdkr \defeq & \lambda W \ldotp\{ \npair{c} \mid
                     \begin{aligned}[t]
                       & \npair{c} \in \stdvr(W) \land \\
                       &  \forall W' \futurewk W, n' < n\ldotp
                       \forall \heapSat[\hs]{n'}{W'} \ldotp \forall \reg, \npair[n']{\reg} \in \stdrr(W') \ldotp \\
                       & \quad \npair[n']{(\reg\update{\pcreg}{\updatePcPerm{\var{c}}},\hs)} \in \observations(W') \}
                 \end{aligned}
\end{align*}

\begin{align*}
  \stder : & \Worlds \nefun \UPred{\Words} \\
  \stder \defeq & \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}
